# Knowledge quiz: Topics 1-3 {.unnumbered}

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(webexercises)
```

```{r, echo = FALSE, results='asis'}
# Uncomment to change widget colours:
#style_widgets(incorrect = "goldenrod", correct = "purple", highlight = "firebrick")
```


Answer the following multiple choice questions to test your understanding of the materials from this module. 

## Questions

**Q1: When did the first global malaria eradication campaign begin?**

```{r q1}
opts_q1 <- 
  sample(c(answer = "1955", 
           "2007",   
           "1896",   
           "1965" ))

```

`r longmcq(opts_q1)`

**Q2: Epidemiologists use a model for studying infectious disease and its spread that involves the microbe that causes the disease, the organism that harbors the disease, and the external factors that cause or allow disease transmission. This is also known as:**

```{r q2}
opts_q2 <- 
  sample(c(answer = "host, agent, and environment", 
           "host, vector, and transmission",   
           "transmission, host, and environment",   
           "organism, transmission, and environment" ))

```

`r longmcq(opts_q2)`

**Q3: Match each term to the correct example:**

|            |             |             |
|------------|-------------|-------------|
| A: Endemic | B: Pandemic | C: Epidemic |

3.1. Malaria is present in Africa at all times becuase of the presence of mosquitos. Malaria is `r fitb(c("A", "Endemic"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")` in Africa.

3.2. The Ebola virus in parts of Africa is in excess of what is expected for this region. This virus is a/an `r fitb(c("C", "Epidemic"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

3.3. Covid-19 is a very recent example of a `r fitb(c("B", "Pandemic"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

**Q4: Choose the correct term to complete this sentence:**

|                 |            |                |
|-----------------|------------|----------------|
| A: Distribution | B: Cluster | C: Determinant |

An outbreak of measles occurred among children at Disney Land in December 2014. This group of cases in this specific time and place can be described as a `r fitb(c("B", "Cluster"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

**Q5: Match each term with its correct definition:**

|                   |               |                         |
|-------------------|---------------|-------------------------|
| A: Incidence rate | B: Prevalence | C: Cumulative Incidence |

-   The proportion of individuals in a population who have a disease at a specific time.`r fitb(c("B", "Prevalence"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

-   The number of new cases of a disease occurring in a specified period.`r fitb(c("A", "Incidence rate"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

-   The proportion of a population with a new event during a given time period.`r fitb(c("C", "Cumulative Incidence"), ignore_ws = TRUE, ignore_case = TRUE, width = "20")`

**Q6: Calculate the incidence rate: A study in a village finds 100 new cases of malaria over a year in a population of 10,000. What is the incidence rate per 1,000 people?**

```{r q6}
opts_q6 <- 
  sample(c(answer = "10 per 1,000", 
           "1 per 1,000",   
           "0.1 per 1,000",   
           "100 per 1,000" ))

```

`r longmcq(opts_q6)`

**Q7: Match the terms to the correct example below:**

-   A study of heart disease comparing a group who eats healthy foods and exercises regularly with one who does not in an effort to test association: `r mcq(c("Descriptive", answer = "Analytic"))`

-   A study to describe the eating habits of adolescents aged 13--18 years in Community X:: `r mcq(c("Analytic", answer = "Descriptive"))`

**Q8: Which of the following is an example of a cohort study?**

```{r q8}
opts_q8 <- 
  sample(c(answer = "Observing a group of individuals over time to see who develops a disease", 
           "Comparing the exposure histories of people with and without a disease",   
           "Conducting a survey to assess the prevalence of a disease",   
           "Describing the characteristics of a single case or a series of cases" ))

```

`r longmcq(opts_q8)`

**Q9: Which of the following is a measure of association in epidemiology?**

```{r q9}
opts_q9 <- 
  sample(c(answer = "Relative risk", 
           "Prevalence",   
           "Incidence",   
           "Point prevalence" ))

```

`r longmcq(opts_q9)`

**Q10: In a case-control study, the measure of association commonly used is:**

```{r q10}
opts_q10 <- 
  sample(c(answer = "Odds ratio", 
           "Risk ratio",   
           "Incidence rate",   
           "Prevalence rate" ))

```

`r longmcq(opts_q10)`

**Q11. Which statement is TRUE about the use of prevalence data in public health?**

```{r q11}
opts_q11 <- 
  sample(c(answer = "It helps assess the burden of disease in a population", 
           "It is used to identify new cases of disease",   
           "It measures the rate of disease over a specific period",   
           "It is not useful for planning health services" ))

```

`r longmcq(opts_q11)`

**Q12. In the context of malaria control, which of the following is an example of a preventive measure?**

```{r q12}
opts_q12 <- 
  sample(c(answer = "Distribution of insecticide-treated bed nets", 
           "Treatment of infected individuals with antimalarial drugs",   
           "Conducting a prevalence survey",   
           "Recording malaria cases in a health information system" ))

```

`r longmcq(opts_q12)`
